---
title: "COVID State Web Scraping"
output: html_document
---

# Set Up

```{r, message = FALSE, warning = FALSE }
library(tidyverse)
library(pdftools)
library(rvest)
library(lubridate)
library(readxl)
source("states.R")
```

# Automated States

- Oklahoma: needs demographic and ages manually entered
- Mississippi: needs age and sex manually entered
- Florida: no manual entry needed, expect long compilation
- Tennessee: no manual entry needed, but needs a date input to function
- North Carolina: needs age manually entered
- District of Columbia: no data on age available
- South Carolina: needs age and sex manually entered
- New Jersey
- New Hampshire
- Guam: no age, sex, race or ethnicity data available

## Troubleshoot States Before Compiling

```{r}
# Check with these first to make sure all states have good data
oklahoma = get_oklahoma()
mississippi = get_mississippi()
florida = get_florida()
tennessee = get_tennessee()
north_carolina = get_north_carolina()
dc = get_dc()
south_carolina = get_south_carolina()
new_jersey = get_new_jersey()
new_hampshire = get_new_hampshire()
guam = get_guam()
```

# Compile The Automated States

```{r}
# Get as much automated data as you can
automated_data_20200514 = compile()
save(compiled_data_20200514, file = "../Data/meta_2020-05-14-cbp.rda")
```

# Manual States

In addition to the information above, we need manual entry for:

- Arizona
- Hawaii
- Idaho
- Iowa
- Kansas (can automate but reading pdf crashes my RStudio?)
- Nevada: no race information
- New York: no demographic information at all
- Puerto Rico: no race data
- South Dakota: have to calculate race counts from case total
- Virgin Island
- West Virginia
- Wyoming

For each of these states, we'll collect sex, age, and race information.

```{r}
manual_data_20200514 = compile_manual_states()
```

```{r}
full_data_20200514 = bind_rows(compiled_data_20200514, manual_data_20200514)
save(full_data_20200514, file = "../Data/meta_2020-05-14-cbp.rda")
```


## TODO:

- standardize Aijins data into your format
- combine Aijins and your data compilation into one
- add some manual data entry into the automated function to capture that extra bit of information that you cant scrape
- my coding is better than yours Aijin