---
title: "COVID State Web Scraping"
output: html_document
---

# Set Up

```{r, message = FALSE, warning = FALSE }
library(tidyverse)
library(pdftools)
library(rvest)
library(lubridate)
library(readxl)
source("states.R")
source("states_constants.R")
```

# Automated States

- Oklahoma: needs demographic and ages manually entered
- Mississippi: needs age and sex manually entered
- Florida: no manual entry needed, expect long compilation
- Tennessee: no manual entry needed, but needs a date input to function
- North Carolina: needs age manually entered
- District of Columbia: no data on age available
- South Carolina: needs age and sex manually entered
- New Jersey
- New Hampshire
- Guam: no age, sex, race or ethnicity data available

## Troubleshoot States Before Compiling

```{r}
# Check with these first to make sure all states have good data
oklahoma = get_oklahoma()
mississippi = get_mississippi()
florida = get_florida()
tennessee = get_tennessee()
north_carolina = get_north_carolina()
south_carolina = get_south_carolina()
new_jersey = get_new_jersey()
new_hampshire = get_new_hampshire()
```

```{r}
# Space for troubleshooting

```

# Compile The Automated States

```{r}
# Get as much automated data as you can
automated_data_20200515 = compile()
```

# Manual States

In addition to the information above, we need manual entry for:

- Arizona
- Hawaii
- Idaho
- Iowa
- Kansas (can automate but reading pdf crashes my RStudio?)
- Nevada: no race information
- New York: no demographic information at all
- South Dakota: have to calculate race counts from case total
- West Virginia
- Wyoming

For each of these states, we'll collect sex, age, and race information.

```{r}
# All the states we do complete manual data entry for

# https://www.azdhs.gov/preparedness/epidemiology-disease-control/infectious-disease-epidemiology/covid-19/dashboards/index.php
arizona = manual_fill(manual_states[1], state_vecs[[1]]) %>% 
      standardize %>% 
      mutate(
        state_name = manual_states[1],
        Link = "https://www.azdhs.gov/preparedness/epidemiology-disease-control/infectious-disease-epidemiology/covid-19/dashboards/index.php",
        platform = "manual",
        comments = "",
        last.update = Sys.time() %>% as_date) %>% 
      select(
        state_name, Link,
        total.tested:hosp_gender,
        platform, comments, last.update)

# https://health.hawaii.gov/coronavirusdisease2019/what-you-should-know/current-situation-in-hawaii/
hawaii = manual_fill(manual_states[2], state_vecs[[2]]) %>% 
  standardize %>% 
  mutate(
    state_name = manual_states[2],
    Link = "https://health.hawaii.gov/coronavirusdisease2019/what-you-should-know/current-situation-in-hawaii/",
    platform = "manual",
    comments = "",
    last.update = Sys.time() %>% as_date) %>% 
  select(
    state_name, Link,
    total.tested:hosp_gender,
    platform, comments, last.update)

# https://public.tableau.com/profile/idaho.division.of.public.health#!/vizhome/DPHIdahoCOVID-19Dashboard_V2/Story1
idaho = manual_fill(manual_states[3], state_vecs[[3]]) %>%
  standardize %>% 
  mutate(
    state_name = manual_states[3],
    Link = "https://public.tableau.com/profile/idaho.division.of.public.health#!/vizhome/DPHIdahoCOVID-19Dashboard_V2/Story1",
    platform = "manual",
    comments = "",
    last.update = Sys.time() %>% as_date) %>% 
  select(
    state_name, Link,
    total.tested:hosp_gender,
    platform, comments, last.update)

# https://coronavirus.iowa.gov/pages/case-counts
iowa = manual_fill(manual_states[4], state_vecs[[4]]) %>% 
  standardize %>% 
  mutate(
    state_name = manual_states[4],
    Link = "https://coronavirus.iowa.gov/pages/case-counts",
    platform = "manual",
    comments = "",
    last.update = Sys.time() %>% as_date) %>% 
  select(
    state_name, Link,
    total.tested:hosp_gender,
    platform, comments, last.update)

# https://www.coronavirus.kdheks.gov/160/COVID-19-in-Kansas
kansas = manual_fill(manual_states[5], state_vecs[[5]]) %>% 
  standardize %>% 
  mutate(
    state_name = manual_states[5],
    Link = "https://www.coronavirus.kdheks.gov/160/COVID-19-in-Kansas",
    platform = "manual",
    comments = "",
    last.update = Sys.time() %>% as_date) %>% 
  select(
    state_name, Link,
    total.tested:hosp_gender,
    platform, comments, last.update)

# https://nvhealthresponse.nv.gov/
nevada = manual_fill(manual_states[6], state_vecs[[6]]) %>% 
      standardize %>% 
      mutate(
        state_name = manual_states[6],
        Link = "https://nvhealthresponse.nv.gov/",
        platform = "manual",
        comments = "",
        last.update = Sys.time() %>% as_date) %>% 
      select(
        state_name, Link,
        total.tested:hosp_gender,
        platform, comments, last.update)

# https://covid19tracker.health.ny.gov/views/NYS-COVID19-Tracker/NYSDOHCOVID-19Tracker-TableView?%3Aembed=yes&%3Atoolbar=no#/views/NYS%2dCOVID19%2dTracker/NYSDOHCOVID%2d19Tracker%2dMap?%253Aembed=yes&%253Atoolbar=no
new_york = manual_fill(manual_states[7], state_vecs[[7]]) %>% 
      standardize %>% 
      mutate(
        state_name = manual_states[7],
        Link = "https://covid19tracker.health.ny.gov/views/NYS-COVID19-Tracker/NYSDOHCOVID-19Tracker-TableView?%3Aembed=yes&%3Atoolbar=no#/views/NYS%2dCOVID19%2dTracker/NYSDOHCOVID%2d19Tracker%2dMap?%253Aembed=yes&%253Atoolbar=no",
        platform = "manual",
        comments = "",
        last.update = Sys.time() %>% as_date) %>% 
      select(
        state_name, Link,
        total.tested:hosp_gender,
        platform, comments, last.update)

# https://doh.sd.gov/news/coronavirus.aspx#SD
south_dakota = manual_fill(manual_states[8], state_vecs[[8]]) %>% 
      standardize %>% 
      mutate(
        state_name = manual_states[8],
        Link = "https://doh.sd.gov/news/coronavirus.aspx#SD",
        platform = "manual",
        comments = "",
        last.update = Sys.time() %>% as_date) %>% 
      select(
        state_name, Link,
        total.tested:hosp_gender,
        platform, comments, last.update)

# https://dhhr.wv.gov/COVID-19/Pages/default.aspx
west_virginia = manual_fill(manual_states[9], state_vecs[[9]]) %>% 
      standardize %>% 
      mutate(
        state_name = manual_states[9],
        Link = "https://dhhr.wv.gov/COVID-19/Pages/default.aspx",
        platform = "manual",
        comments = "",
        last.update = Sys.time() %>% as_date) %>% 
      select(
        state_name, Link,
        total.tested:hosp_gender,
        platform, comments, last.update)

# https://health.wyo.gov/publichealth/infectious-disease-epidemiology-unit/disease/novel-coronavirus/covid-19-map-and-statistics/
wyoming = manual_fill(manual_states[10], state_vecs[[10]]) %>% 
      standardize %>% 
      mutate(
        state_name = manual_states[10],
        Link = "https://health.wyo.gov/publichealth/infectious-disease-epidemiology-unit/disease/novel-coronavirus/covid-19-map-and-statistics/",
        platform = "manual",
        comments = "",
        last.update = Sys.time() %>% as_date) %>% 
      select(
        state_name, Link,
        total.tested:hosp_gender,
        platform, comments, last.update)
    
manual_data_20200515 = bind_rows(
  arizona,
  hawaii,
  idaho,
  iowa,
  kansas,
  nevada,
  new_york,
  south_dakota,
  west_virginia,
  wyoming)
```

```{r}
full_data_20200515 = bind_rows(automated_data_20200515, manual_data_20200515)
save(full_data_20200515, file = "../Data/meta_2020-05-15-cbp.rda")
```

# Data Separation

```{r}
full_data = read_csv("../Data/meta_final_2020-05-16.csv") %>% 
  mutate(
    total_test = unlist(map(total.tested, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        total = data %>% str_split(";", simplify = TRUE) %>% .[1,1]
        return(as.numeric(total))
      } else {
        as.numeric(data)
      }
    })),
    total_case = unlist(map(total.case, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        total = data %>% str_split(";", simplify = TRUE) %>% .[1,1]
        return(as.numeric(total))
      } else {
        as.numeric(data)
      }
    })),
    total_death = unlist(map(total.death, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        total = data %>% str_split(";", simplify = TRUE) %>% .[1,1]
        return(as.numeric(total))
      } else {
        as.numeric(data)
      }
    })),
    total_hosp = unlist(map(total_hosp, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        total = data %>% str_split(";", simplify = TRUE) %>% .[1,1]
        return(as.numeric(total))
      } else {
        as.numeric(data)
      }
    }))
  )

# Dealing with cases first
final_case_data = full_data %>% 
  select(state_name, 
         total_test,
         total_case, 
         total_death, 
         total_hosp,
         positive_age, 
         positive_race, 
         positive_gender) %>% 
  mutate(
    case_by_age = map(positive_age, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        age_tib = data %>% 
          str_split(";", simplify = TRUE) %>% 
          str_split(":", simplify = TRUE) %>% 
          as_tibble()
        colnames(age_tib) = c("category", "count")
        age_tib %>% 
          mutate(
            category = str_trim(category),
            count = as.numeric(count)
          )
      }
    }),
    case_by_race = map(positive_race, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        race_tib = data %>% 
          str_split(";", simplify = TRUE) %>% 
          str_split(":", simplify = TRUE) %>% 
          as_tibble()
        colnames(race_tib) = c("category", "count")
        race_tib %>% 
          mutate(
            category = str_trim(category),
            count = str_replace(count, ",", "") %>%  as.numeric(count)
          )
      }
    }),
    case_by_sex = map(positive_gender, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        sex_tib = data %>% 
          str_split(";", simplify = TRUE) %>% 
          str_split(":", simplify = TRUE) %>% 
          as_tibble()
        colnames(sex_tib) = c("category", "count")
        sex_tib %>% 
          mutate(
            category = str_trim(category),
            count = str_replace(count, ",", "") %>%  as.numeric(count)
          )
      }
    })
  ) %>% 
  select(
    state_name, 
    total_test,
    total_case, 
    total_death, 
    total_hosp,
    case_by_age,
    case_by_race,
    case_by_sex
    ) 

case_age_data = final_case_data %>% 
  select(state_name, total_test, total_case, total_death, total_hosp, case_by_age) %>% 
  unnest_wider(case_by_age) %>% 
  unnest(c(category, count)) %>% 
  select(-`...1`) %>% 
  mutate( 
    strata_type = "age",
    data_type = "case"
    )

case_race_data = final_case_data %>% 
  select(state_name, total_test, total_case, total_death, total_hosp, case_by_race) %>% 
  unnest_wider(case_by_race) %>% 
  unnest(c(category, count)) %>% 
  select(-`...1`) %>% 
  mutate( 
    strata_type = "race",
    data_type = "case" 
    )

case_sex_data = final_case_data %>% 
  select(state_name, total_test, total_case, total_death, total_hosp, case_by_sex) %>% 
  unnest_wider(case_by_sex) %>% 
  unnest(c(category, count)) %>% 
  select(-`...1`) %>% 
  mutate( 
    strata_type = "sex",
    data_type = "case" 
    )
```

```{r}
# Dealing with deaths
final_death_data = full_data %>% 
  select(state_name, 
         total_test,
         total_case, 
         total_death, 
         total_hosp,
         death_age, 
         death_race, 
         death_gender) %>% 
  mutate(
    death_by_age = map(death_age, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        age_tib = data %>% 
          str_split(";", simplify = TRUE) %>% 
          str_split(":", simplify = TRUE) %>% 
          as_tibble()
        colnames(age_tib) = c("category", "count")
        age_tib %>% 
          mutate(
            category = str_trim(category),
            count = as.numeric(count)
          )
      }
    }),
    death_by_race = map(death_race, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        race_tib = data %>% 
          str_split(";", simplify = TRUE) %>% 
          str_split(":", simplify = TRUE) %>% 
          as_tibble()
        colnames(race_tib) = c("category", "count")
        race_tib %>% 
          mutate(
            category = str_trim(category),
            count = str_replace(count, ",", "") %>%  as.numeric(count)
          )
      }
    }),
    death_by_sex = map(death_gender, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        sex_tib = data %>% 
          str_split(";", simplify = TRUE) %>% 
          str_split(":", simplify = TRUE) %>% 
          as_tibble()
        colnames(sex_tib) = c("category", "count")
        sex_tib %>% 
          mutate(
            category = str_trim(category),
            count = str_replace(count, ",", "") %>%  as.numeric(count)
          )
      }
    })
  ) %>% 
  select(
    state_name, 
    total_test, 
    total_case, 
    total_death, 
    total_hosp,
    death_by_race,
    death_by_age,
    death_by_sex
    ) 

death_age_data = final_death_data %>% 
  select(state_name, total_test, total_case, total_death, total_hosp, death_by_age) %>% 
  unnest_wider(death_by_age) %>% 
  unnest(c(category, count)) %>% 
  select(-`...1`) %>% 
  mutate( 
    strata_type = "age",
    data_type = "death"
    )

death_race_data = final_death_data %>% 
  select(state_name, total_test, total_case, total_death, total_hosp, death_by_race) %>% 
  unnest_wider(death_by_race) %>% 
  unnest(c(category, count)) %>% 
  select(-`...1`) %>% 
  mutate( 
    strata_type = "race",
    data_type = "death"
    )

death_sex_data = final_death_data %>% 
  select(state_name, total_test, total_case, total_death, total_hosp, death_by_sex) %>% 
  unnest_wider(death_by_sex) %>% 
  unnest(c(category, count)) %>% 
  select(-`...1`) %>% 
  mutate( 
    strata_type = "sex",
    data_type = "death" 
    )
```

```{r}
# Handling data for hospitalizations
final_hosp_data = full_data %>% 
  select(state_name, 
         total_test,
         total_case, 
         total_death, 
         total_hosp, 
         hosp_age, 
         hosp_race, 
         hosp_gender) %>% 
  mutate(
    hosp_by_age = map(hosp_age, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        age_tib = data %>% 
          str_split(";", simplify = TRUE) %>% 
          str_split(":", simplify = TRUE) %>% 
          as_tibble()
        colnames(age_tib) = c("category", "count")
        age_tib %>% 
          mutate(
            category = str_trim(category),
            count = as.numeric(count)
          )
      }
    }),
    hosp_by_race = map(hosp_race, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        race_tib = data %>% 
          str_split(";", simplify = TRUE) %>% 
          str_split(":", simplify = TRUE) %>% 
          as_tibble()
        colnames(race_tib) = c("category", "count")
        race_tib %>% 
          mutate(
            category = str_trim(category),
            count = str_replace(count, ",", "") %>%  as.numeric(count)
          )
      }
    }),
    hosp_by_sex = map(hosp_gender, function(data) {
      if (is.na(data)) {
        return(NA)
      } else if (str_detect(data, ";")) {
        sex_tib = data %>% 
          str_split(";", simplify = TRUE) %>% 
          str_split(":", simplify = TRUE) %>% 
          as_tibble()
        colnames(sex_tib) = c("category", "count")
        sex_tib %>% 
          mutate(
            category = str_trim(category),
            count = str_replace(count, ",", "") %>%  as.numeric(count)
          )
      }
    })
  ) %>% 
  select(
    state_name, 
    total_test, 
    total_case, 
    total_death, 
    total_hosp,
    hosp_by_race,
    hosp_by_age,
    hosp_by_sex
    ) 

hosp_age_data = final_hosp_data %>% 
  select(state_name, total_test, total_case, total_death, total_hosp, hosp_by_age) %>% 
  unnest_wider(hosp_by_age) %>% 
  unnest(c(category, count)) %>% 
  select(-`...1`) %>% 
  mutate( 
    strata_type = "hosp",
    data_type = "age"
    )

hosp_race_data = final_hosp_data %>% 
  select(state_name, total_test, total_case, total_death, total_hosp, hosp_by_race) %>% 
  unnest_wider(hosp_by_race) %>% 
  unnest(c(category, count)) %>% 
  select(-`...1`) %>% 
  mutate( 
    strata_type = "hosp",
    data_type = "race"
    )

hosp_sex_data = final_hosp_data %>% 
  select(state_name, total_test, total_case, total_death, total_hosp, hosp_by_sex) %>% 
  unnest_wider(hosp_by_sex) %>% 
  unnest(c(category, count)) %>% 
  select(-`...1`) %>% 
  mutate( 
    strata_type = "hosp",
    data_type = "sex"
    )
```

## Save To CSV

```{r}
final = bind_rows(
  case_age_data,
  case_race_data,
  case_sex_data,
  death_age_data,
  death_race_data,
  death_sex_data,
  hosp_age_data,
  hosp_race_data,
  hosp_sex_data) 

write.csv(final, "../Data/processed_state_data_20200514.csv")
```


