---
title: "Data Harmonization"
author: "Christian Pascual"
output: html_document
---

# Purpose Of Notebook

Create a visualization that shows trends in age and race between two states, in face of different ways of collecting these data

```{r, message = FALSE, warning = FALSE }
library(tidyverse)
library(pdftools)
library(rvest)
library(lubridate)
library(readxl)
```

# Helper Functions

```{r}
default_cols = c(
    "total",
    "age_0_19", 
    "age_20_29", 
    "age_30_39", 
    "age_40_49",
    "age_50_59", 
    "age_60_69", 
    "age_70_79", 
    "age_80+", 
    "age_unk",
    "sex_male", 
    "sex_female", 
    "sex_unk",
    "ethnicity_hispanic", 
    "ethnicity_non_hispanic",
    "ethnicity_unk",
    "race_white", 
    "race_AfrA",
    "race_NatA",
    "race_asian", 
    "race_other",
    "race_multi", 
    "race_unk")

# Helper functions for data cleaning
skeleton_col = function(subdivs) {
  # Need to make a named vector to make it easier to insert data
  # in a cel-wise fashion
  
  # subdivs should contain all of the relevant information that
  # a state provides on their websitE
  
  skeleton = vector(mode = "list", length = length(subdivs))
  names(skeleton) = subdivs
  return(skeleton)
}
skeleton_table = function(subdivs) {
  # Create a table of blanks using named vectors
  # Easy insert of data
  skeleton = list(
    "data" = names(skeleton_col(subdivs)),
    "tested" = skeleton_col(subdivs),
    "cases" = skeleton_col(subdivs),
    "negatives" = skeleton_col(subdivs),
    "recovered" = skeleton_col(subdivs),
    "deaths" = skeleton_col(subdivs),
    "hospitalized" = skeleton_col(subdivs))
  return(skeleton)
}
```

# Bringing In Data

Using Florida and Tennessee as example states since I have the functions for those:

```{r, echo = FALSE }
# Changing columns to fit specific age brackets
fl_cols = c(
    "total",
    "age_0_4", 
    "age_5_14", 
    "age_15_24", 
    "age_25_34",
    "age_35_44", 
    "age_45_54", 
    "age_55_64", 
    "age_65_74", 
    "age_75_84", 
    "age_85+", 
    "age_unk",
    "sex_male", 
    "sex_female", 
    "sex_unk",
    "ethnicity_hispanic", 
    "ethnicity_non_hispanic",
    "ethnicity_unk",
    "race_white", 
    "race_AfrA",
    "race_NatA",
    "race_asian", 
    "race_other",
    "race_multi", 
    "race_unk")

get_florida = function(pdf_url) {
  # Get pdf from: https://www.floridadisaster.org/covid19/covid-19-data-reports/
  url = "https://www.floridadisaster.org/covid19/covid-19-data-reports/"
  
  pdf_path = read_html(url) %>% 
    html_nodes("body .l-surround #mainContent #text-page-wrap .row") %>% 
    html_nodes("#mainContent .main-column p a") %>% html_attr("href") %>% .[1]
  # Index 1 gets the first pdf in the list, presumed to be the most recent
  
  pdf_url = paste0("https://www.floridadisaster.org/", pdf_path)
  data = pdf_text(pdf_url)
  
  # Demographic data is on
  demographic_data = data %>% .[3] %>% 
    str_split(., "\n") %>% .[[1]] %>% 
    str_squish()
  
  # Initialize skeleton
  skeleton = skeleton_table(fl_cols)
  
  tested = data %>% .[1] %>% 
    str_split(., "\n") %>% .[[1]] %>% 
    str_squish() %>% .[[22]] %>% 
    str_split(., " ", simplify = TRUE) %>% .[1, 3] %>% 
    str_replace(., ",", "") %>% as.numeric()
  
  negatives = data %>% .[1] %>% 
    str_split(., "\n") %>% .[[1]] %>% 
    str_squish() %>% .[[25]] %>% 
    str_split(., " ", simplify = TRUE) %>% .[1, 2] %>% 
    str_replace(., ",", "") %>% as.numeric()
  
  cases = demographic_data %>% .[16] %>% 
    str_split(., " ", simplify = TRUE) %>% .[1, 2] %>% 
    str_replace(., ",", "") %>% as.numeric()
  
  deaths = demographic_data %>% .[16] %>% 
    str_split(., " ", simplify = TRUE) %>% .[1, 4] %>% 
    str_replace(., ",", "") %>% as.numeric()
  
  
  males = demographic_data %>% .[5] %>% 
    str_split(., " ", simplify = TRUE) %>%  .[1, 10] %>% 
    str_replace(., ",", "") %>% as.numeric()
  
  # Each row contains data on cases, hosp and death
  between_0_and_4 = demographic_data %>% .[5] %>% 
    str_split(., " ", simplify = TRUE)
  
  between_0_and_4_case = between_0_and_4 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  between_0_and_4_hosp = between_0_and_4 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  between_0_and_4_death = between_0_and_4 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  between_5_and_14 = demographic_data %>% .[6] %>% 
    str_split(., " ", simplify = TRUE)

  between_5_and_14_case = between_5_and_14 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  between_5_and_14_hosp = between_5_and_14 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  between_5_and_14_death = between_5_and_14 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  between_15_and_24 = demographic_data %>% .[7] %>% 
    str_split(., " ", simplify = TRUE)
  
  between_15_and_24_case = between_15_and_24 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  between_15_and_24_hosp = between_15_and_24 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  between_15_and_24_death = between_15_and_24 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  between_25_and_34 = demographic_data %>% .[8] %>% 
    str_split(., " ", simplify = TRUE)
  
  between_25_and_34_case = between_25_and_34 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  between_25_and_34_hosp = between_25_and_34 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  between_25_and_34_death = between_25_and_34 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  between_35_and_44 = demographic_data %>% .[9] %>% 
    str_split(., " ", simplify = TRUE)
  
  between_35_and_44_case = between_35_and_44 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  between_35_and_44_hosp = between_35_and_44 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  between_35_and_44_death = between_35_and_44 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  between_45_and_54 = demographic_data %>% .[10] %>% 
    str_split(., " ", simplify = TRUE)
  
  between_45_and_54_case = between_45_and_54 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  between_45_and_54_hosp = between_45_and_54 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  between_45_and_54_death = between_45_and_54 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  between_55_and_64 = demographic_data %>% .[11] %>% 
    str_split(., " ", simplify = TRUE)
  
  between_55_and_64_case = between_55_and_64 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  between_55_and_64_hosp = between_55_and_64 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  between_55_and_64_death = between_55_and_64 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  between_65_and_74 = demographic_data %>% .[12] %>% 
    str_split(., " ", simplify = TRUE)
  
  between_65_and_74_case = between_65_and_74 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  between_65_and_74_hosp = between_65_and_74 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  between_65_and_74_death = between_65_and_74 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  between_75_and_84 = demographic_data %>% .[13] %>% 
    str_split(., " ", simplify = TRUE)
  
  between_75_and_84_case = between_75_and_84 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  between_75_and_84_hosp = between_75_and_84 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  between_75_and_84_death = between_75_and_84 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  older_than_85 = demographic_data %>% .[14] %>% 
    str_split(., " ", simplify = TRUE)
  
  older_than_85_case = older_than_85 %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  older_than_85_hosp = older_than_85 %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  older_than_85_death = older_than_85 %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  unknown_age = demographic_data %>% .[15] %>% 
    str_split(., " ", simplify = TRUE)
  
  unknown_age_case = unknown_age %>% .[1, 2] %>% 
    str_replace(",","") %>% as.numeric
  unknown_age_hosp = unknown_age %>% .[1, 4] %>% 
    str_replace(",","") %>% as.numeric
  unknown_age_death = unknown_age %>% .[1, 6] %>% 
    str_replace(",","") %>% as.numeric
  
  hispanic = demographic_data %>% .[18] %>% 
    str_split(., " ", simplify = TRUE)
  
  hispanic_case = hispanic %>% .[1, 2] %>% 
    str_replace(",","") %>% as.numeric
  hispanic_hosp = hispanic %>% .[1, 4] %>% 
    str_replace(",","") %>% as.numeric
  hispanic_death = hispanic %>% .[1, 6] %>% 
    str_replace(",","") %>% as.numeric
  
  non_hispanic = demographic_data %>% .[19] %>% 
    str_split(., " ", simplify = TRUE)
  
  non_hispanic_case = non_hispanic %>% .[1, 2] %>% 
    str_replace(",","") %>% as.numeric
  non_hispanic_hosp = non_hispanic %>% .[1, 4] %>% 
    str_replace(",","") %>% as.numeric
  non_hispanic_death = non_hispanic %>% .[1, 6] %>% 
    str_replace(",","") %>% as.numeric
  
  unknown_ethnicity = demographic_data %>% .[20] %>% 
    str_split(., " ", simplify = TRUE)
  
  unknown_ethnicity_case = unknown_ethnicity %>% .[1, 2] %>% 
    str_replace(",","") %>% as.numeric
  unknown_ethnicity_hosp = unknown_ethnicity %>% .[1, 4] %>% 
    str_replace(",","") %>% as.numeric
  unknown_ethnicity_death = unknown_ethnicity %>% .[1, 6] %>% 
    str_replace(",","") %>% as.numeric
  
  white = demographic_data %>% .[23] %>% 
    str_split(., " ", simplify = TRUE)
  
  white_case = white %>% .[1, 2] %>% 
    str_replace(",","") %>% as.numeric
  white_hosp = white %>% .[1, 4] %>% 
    str_replace(",","") %>% as.numeric
  white_death = white %>% .[1, 6] %>% 
    str_replace(",","") %>% as.numeric
  
  black = demographic_data %>% .[27] %>% 
    str_split(., " ", simplify = TRUE) 
  
  black_case = black %>% .[1, 2] %>% 
    str_replace(",","") %>% as.numeric
  black_hosp = black %>% .[1, 4] %>% 
    str_replace(",","") %>% as.numeric
  black_death = black %>% .[1, 6] %>% 
    str_replace(",","") %>% as.numeric
  
  other_race = demographic_data %>% .[31] %>% 
    str_split(., " ", simplify = TRUE) 
  
  other_race_case = other_race %>% .[1, 2] %>% 
    str_replace(",","") %>% as.numeric
  other_race_hosp = other_race %>% .[1, 4] %>% 
    str_replace(",","") %>% as.numeric
  other_race_death = other_race %>% .[1, 6] %>% 
    str_replace(",","") %>% as.numeric
  
  unk_race = demographic_data %>% .[35] %>% 
    str_split(., " ", simplify = TRUE)

  unk_race_case = unk_race %>% .[1, 3] %>% 
    str_replace(",","") %>% as.numeric
  unk_race_hosp = unk_race %>% .[1, 5] %>% 
    str_replace(",","") %>% as.numeric
  unk_race_death = unk_race %>% .[1, 7] %>% 
    str_replace(",","") %>% as.numeric
  
  # Log all of the information
  skeleton[["tested"]][["total"]] = tested
  skeleton[["negatives"]][["total"]] = negatives
  
  skeleton[["cases"]][["total"]] = cases
  
  skeleton[["cases"]][["sex_male"]] = males
  skeleton[["cases"]][["sex_female"]] = cases - males
  
  skeleton[["cases"]][["age_0_4"]] = between_0_and_4_case
  skeleton[["cases"]][["age_5_14"]] = between_5_and_14_case
  skeleton[["cases"]][["age_15_24"]] = between_15_and_24_case
  skeleton[["cases"]][["age_25_34"]] = between_25_and_34_case
  skeleton[["cases"]][["age_35_44"]] = between_35_and_44_case
  skeleton[["cases"]][["age_45_54"]] = between_45_and_54_case
  skeleton[["cases"]][["age_55_64"]] = between_55_and_64_case
  skeleton[["cases"]][["age_65_74"]] = between_65_and_74_case
  skeleton[["cases"]][["age_75_84"]] = between_75_and_84_case
  skeleton[["cases"]][["age_85+"]] = older_than_85_case
  skeleton[["cases"]][["age_unk"]] = unknown_age_case
  skeleton[["cases"]][["ethnicity_hispanic"]] = hispanic_case
  skeleton[["cases"]][["ethnicity_non_hispanic"]] = non_hispanic_case
  skeleton[["cases"]][["ethnicity_unk"]] = unknown_ethnicity_case
  skeleton[["cases"]][["race_white"]] = white_case
  skeleton[["cases"]][["race_AfrA"]] = black_case
  skeleton[["cases"]][["race_other"]] = other_race_case
  skeleton[["cases"]][["race_unk"]] = unk_race_case

  skeleton[["hospitalized"]][["age_0_4"]] = between_0_and_4_hosp
  skeleton[["hospitalized"]][["age_5_14"]] = between_5_and_14_hosp
  skeleton[["hospitalized"]][["age_15_24"]] = between_15_and_24_hosp
  skeleton[["hospitalized"]][["age_25_34"]] = between_25_and_34_hosp
  skeleton[["hospitalized"]][["age_35_44"]] = between_35_and_44_hosp
  skeleton[["hospitalized"]][["age_45_54"]] = between_45_and_54_hosp
  skeleton[["hospitalized"]][["age_55_64"]] = between_55_and_64_hosp
  skeleton[["hospitalized"]][["age_65_74"]] = between_65_and_74_hosp
  skeleton[["hospitalized"]][["age_75_84"]] = between_75_and_84_hosp
  skeleton[["hospitalized"]][["age_85+"]] = older_than_85_hosp
  skeleton[["hospitalized"]][["age_unk"]] = unknown_age_hosp
  skeleton[["hospitalized"]][["ethnicity_hispanic"]] = hispanic_hosp
  skeleton[["hospitalized"]][["ethnicity_non_hispanic"]] = non_hispanic_hosp
  skeleton[["hospitalized"]][["ethnicity_unk"]] = unknown_ethnicity_hosp
  skeleton[["hospitalized"]][["race_white"]] = white_hosp
  skeleton[["hospitalized"]][["race_AfrA"]] = black_hosp
  skeleton[["hospitalized"]][["race_other"]] = other_race_hosp
  skeleton[["hospitalized"]][["race_unk"]] = unk_race_hosp
  
  skeleton[["deaths"]][["total"]] = deaths
  skeleton[["deaths"]][["age_0_4"]] = between_0_and_4_death
  skeleton[["deaths"]][["age_5_14"]] = between_5_and_14_death
  skeleton[["deaths"]][["age_15_24"]] = between_15_and_24_death
  skeleton[["deaths"]][["age_25_34"]] = between_25_and_34_death
  skeleton[["deaths"]][["age_35_44"]] = between_35_and_44_death
  skeleton[["deaths"]][["age_45_54"]] = between_45_and_54_death
  skeleton[["deaths"]][["age_55_64"]] = between_55_and_64_death
  skeleton[["deaths"]][["age_65_74"]] = between_65_and_74_death
  skeleton[["deaths"]][["age_75_84"]] = between_75_and_84_death
  skeleton[["deaths"]][["age_85+"]] = older_than_85_death
  skeleton[["deaths"]][["age_unk"]] = unknown_age_death
  skeleton[["deaths"]][["ethnicity_hispanic"]] = hispanic_death
  skeleton[["deaths"]][["ethnicity_non_hispanic"]] = non_hispanic_death
  skeleton[["deaths"]][["ethnicity_unk"]] = unknown_ethnicity_death
  skeleton[["deaths"]][["race_white"]] = white_death
  skeleton[["deaths"]][["race_AfrA"]] = black_death
  skeleton[["deaths"]][["race_other"]] = other_race_death
  skeleton[["deaths"]][["race_unk"]] = unk_race_death
  
  return(list(
    data = as_tibble(skeleton),
    comments = list()
  ))
}
```

```{r, echo = FALSE}
tn_cols = c(
    "total",
    "age_0_10", 
    "age_11_20", 
    "age_21_30",
    "age_31_40",
    "age_41_50",
    "age_51_60",
    "age_61_70",
    "age_71_80",
    "age_81+", 
    "age_unk",
    "sex_male", 
    "sex_female", 
    "sex_unk",
    "ethnicity_hispanic", 
    "ethnicity_non_hispanic",
    "ethnicity_unk",
    "race_white", 
    "race_AfrA",
    "race_NatA",
    "race_asian", 
    "race_other",
    "race_multi", 
    "race_unk")

get_tennessee = function(date) {
  
  # Scrape the website to get to the datasets by their source link
  url = "https://www.tn.gov/health/cedep/ncov/data/downloadable-datasets.html"
  
  xlsx_paths = read_html(url) %>% 
    html_nodes("body #main .row .col-lg-8 article div .tn-panel .panel") %>% 
    html_nodes("div .tn-rte p a") %>% 
    html_attr("href")

  age_temp = tempfile(fileext = ".xlsx")
  case_temp = tempfile(fileext = ".xlsx")
  demo_temp = tempfile(fileext = ".xlsx")
  
  age_url = paste0("https://www.tn.gov", xlsx_paths[1])
  case_url = paste0("https://www.tn.gov", xlsx_paths[3])
  demo_url = paste0("https://www.tn.gov", xlsx_paths[5])
  
  
  download.file(age_url, destfile = age_temp, mode = 'wb')
  download.file(case_url, destfile = case_temp, mode = 'wb')
  download.file(demo_url, destfile = demo_temp, mode = 'wb')
  
  age_data = read_excel(age_temp, sheet = 1) %>% 
    filter(DATE == as_date(date))
  case_data = read_excel(case_temp, sheet = 1) %>% 
    filter(DATE == as_date(date))
  demo_data = read_excel(demo_temp, sheet = 1) %>% 
    filter(Date == as_date(date))
  
  skeleton = skeleton_table(tn_cols)
  
  tests = case_data %>% pull(TOTAL_TESTS)
  cases = case_data %>% pull(TOTAL_CASES)
  negatives = case_data %>% pull(NEG_TESTS)
  deaths = case_data %>% pull(TOTAL_DEATHS)
  recovered = case_data %>% pull(TOTAL_RECOVERED)
  
  ar_cases = age_data %>% pull(AR_CASECOUNT)
  ar_deaths = age_data %>% pull(AR_TOTALDEATHS)
  
  race_cases = demo_data %>% filter(Category == "RACE")
  ethnicity_cases = demo_data %>% filter(Category == "ETHNICITY") 
  sex_cases = demo_data %>% filter(Category == "SEX")
  
  race_deaths = demo_data %>% filter(Category == "RACE")
  ethnicity_deaths = demo_data %>% filter(Category == "ETHNICITY")
  sex_deaths = demo_data %>% filter(Category == "SEX")

  # Log all the data from the Excel sheet
  skeleton[["tested"]][["total"]] = tests
  
  skeleton[["cases"]][["total"]] = cases
  skeleton[["cases"]][["age_0_10"]] = ar_cases[1] 
  skeleton[["cases"]][["age_11_20"]] = ar_cases[2]
  skeleton[["cases"]][["age_21_30"]] = ar_cases[3]
  skeleton[["cases"]][["age_31_40"]] = ar_cases[4]
  skeleton[["cases"]][["age_41_50"]] = ar_cases[5]
  skeleton[["cases"]][["age_51_60"]] = ar_cases[6]
  skeleton[["cases"]][["age_61_70"]] = ar_cases[7]
  skeleton[["cases"]][["age_71_80"]] = ar_cases[8]
  skeleton[["cases"]][["age_81+"]] = ar_cases[9]
  skeleton[["cases"]][["age_unk"]] = ar_cases[10]
  skeleton[["cases"]][["sex_male"]] = sex_cases %>% 
    filter(Cat_Detail == "Male") %>% pull(Cat_CaseCount) 
  skeleton[["cases"]][["sex_female"]] = sex_cases %>% 
    filter(Cat_Detail == "Female") %>% pull(Cat_CaseCount) 
  skeleton[["cases"]][["sex_unk"]] = sex_cases %>% 
    filter(Cat_Detail == "Pending") %>% pull(Cat_CaseCount) 
  skeleton[["cases"]][["race_white"]] = race_cases %>% 
    filter(Cat_Detail == "White") %>% pull(Cat_CaseCount) 
  skeleton[["cases"]][["race_AfrA"]] = race_cases %>% 
    filter(Cat_Detail == "Black or African American") %>% pull(Cat_CaseCount) 
  skeleton[["cases"]][["race_other"]] = race_cases %>% 
    filter(Cat_Detail == "Other/Multiracial") %>% pull(Cat_CaseCount)
  skeleton[["cases"]][["race_asian"]] = race_cases %>% 
    filter(Cat_Detail == "Asian") %>% pull(Cat_CaseCount) 
  skeleton[["cases"]][["race_unk"]] = race_cases %>% 
    filter(Cat_Detail == "Pending") %>% pull(Cat_CaseCount) 
  skeleton[["cases"]][["ethnicity_hispanic"]] = ethnicity_cases %>% 
    filter(Cat_Detail == "Hispanic") %>% pull(Cat_CaseCount)
  skeleton[["cases"]][["ethnicity_non_hispanic"]] = ethnicity_cases %>% 
    filter(Cat_Detail == "Not Hispanic or Latino") %>% pull(Cat_CaseCount)
  skeleton[["cases"]][["ethnicity_unk"]] = ethnicity_cases %>% 
    filter(Cat_Detail == "Pending") %>% pull(Cat_CaseCount)
  
  skeleton[["negatives"]][["total"]] = negatives
  
  skeleton[["deaths"]][["total"]] = deaths
  skeleton[["deaths"]][["age_0_10"]] = ar_deaths[1] 
  skeleton[["deaths"]][["age_11_20"]] = ar_deaths[2]
  skeleton[["deaths"]][["age_21_30"]] = ar_deaths[3]
  skeleton[["deaths"]][["age_31_40"]] = ar_deaths[4]
  skeleton[["deaths"]][["age_41_50"]] = ar_deaths[5]
  skeleton[["deaths"]][["age_51_60"]] = ar_deaths[6]
  skeleton[["deaths"]][["age_61_70"]] = ar_deaths[7]
  skeleton[["deaths"]][["age_71_80"]] = ar_deaths[8]
  skeleton[["deaths"]][["age_81+"]] = ar_deaths[9]
  skeleton[["deaths"]][["age_unk"]] = ar_deaths[10]
  skeleton[["deaths"]][["sex_male"]] = sex_deaths %>% 
    filter(Cat_Detail == "Male") %>% pull(CAT_DEATHCOUNT) 
  skeleton[["deaths"]][["sex_female"]] = sex_deaths %>% 
    filter(Cat_Detail == "Female") %>% pull(CAT_DEATHCOUNT) 
  skeleton[["deaths"]][["sex_unk"]] = sex_deaths %>% 
    filter(Cat_Detail == "Pending") %>% pull(CAT_DEATHCOUNT) 
  skeleton[["deaths"]][["race_white"]] = race_deaths %>% 
    filter(Cat_Detail == "White") %>% pull(CAT_DEATHCOUNT) 
  skeleton[["deaths"]][["race_AfrA"]] = race_deaths %>% 
    filter(Cat_Detail == "Black or African American") %>% pull(CAT_DEATHCOUNT) 
  skeleton[["deaths"]][["race_other"]] = race_deaths %>% 
    filter(Cat_Detail == "Other/Multiracial") %>% pull(CAT_DEATHCOUNT)
  skeleton[["deaths"]][["race_asian"]] = race_deaths %>% 
    filter(Cat_Detail == "Asian") %>% pull(CAT_DEATHCOUNT) 
  skeleton[["deaths"]][["race_unk"]] = race_deaths %>% 
    filter(Cat_Detail == "Pending") %>% pull(CAT_DEATHCOUNT) 
  skeleton[["deaths"]][["ethnicity_hispanic"]] = ethnicity_deaths %>% 
    filter(Cat_Detail == "Hispanic") %>% pull(CAT_DEATHCOUNT)
  skeleton[["deaths"]][["ethnicity_non_hispanic"]] = ethnicity_deaths %>% 
    filter(Cat_Detail == "Not Hispanic or Latino") %>% pull(CAT_DEATHCOUNT)
  skeleton[["deaths"]][["ethnicity_unk"]] = ethnicity_deaths %>% 
    filter(Cat_Detail == "Pending") %>% pull(CAT_DEATHCOUNT)
  
  skeleton[["recovered"]][["total"]] = recovered
  
  return(list(
    data = as_tibble(skeleton),
    comments = list()
    ))
}
```

```{r}
florida = get_florida() %>% 
  .$data %>% select(data, cases)
tennessee = get_tennessee("2020-05-09") %>% 
  .$data %>% select(data, cases)
```

# Age Harmonization

Age is still numeric, so that will be the x-axis. To express the different bounds, we'll show an age bound for each age and state. In order to plot it, we'll just use the midpoint of this bound. Upper age brackets like 85+ limits will be shown at that point (85). Unknown age will be set to 100.

```{r}
fl_ages = florida %>% 
  filter(
    data %in% c("age_0_4", "age_5_14", "age_15_24", 
                "age_25_34", "age_35_44", "age_45_54", 
                "age_55_64", "age_65_74", "age_75_84", 
                "age_85+", "age_unk")) %>% 
  mutate(
    bounds = map(data, function(s) {
      str_split(s, "_") %>% unlist %>% .[-1] %>% unlist
      }),
    left_bound = map_dbl(bounds, function(b) {
      if (length(b) == 2) {
        b[1] %>% as.numeric
      } else if (str_detect(b, "\\+")) {
        b %>% str_replace("\\+", "") %>% as.numeric
      } else {
        100 # default to 100 to show unknown on graph
      }
    }),
    right_bound = map_dbl(bounds, function(b) {
      if (length(b) == 2) {
        b[2] %>% as.numeric
      } else if (str_detect(b, "\\+")) {
        b %>% str_replace("\\+", "") %>% as.numeric
      } else {
        100 # default to 100 to show unknown on graph
      }
    }),
    mid = (left_bound + right_bound) / 2,
    state = "Florida"
  )

tn_ages = tennessee %>% 
  filter(
    data %in% c("age_0_10", "age_11_20", "age_21_30",
                "age_31_40", "age_41_50", "age_51_60",
                "age_61_70", "age_71_80", "age_81+", 
                "age_unk")) %>% 
  mutate(
    bounds = map(data, function(s) {
      str_split(s, "_") %>% unlist %>% .[-1] %>% unlist
      }),
    left_bound = map_dbl(bounds, function(b) {
      if (length(b) == 2) {
        b[1] %>% as.numeric
      } else if (str_detect(b, "\\+")) {
        b %>% str_replace("\\+", "") %>% as.numeric
      } else {
        100 # default to 100 to show unknown on graph
      }
    }),
    right_bound = map_dbl(bounds, function(b) {
      if (length(b) == 2) {
        b[2] %>% as.numeric
      } else if (str_detect(b, "\\+")) {
        b %>% str_replace("\\+", "") %>% as.numeric
      } else {
        100 # default to 100 to show unknown on graph
      }
    }),
    mid = (left_bound + right_bound) / 2,
    state = "Tennessee"
  )

final_data = bind_rows(fl_ages, tn_ages) %>% 
  mutate(
    cases = unlist(cases),
    state = factor(state),
    bracket_line = if_else(state == "Florida", -500, -1000)
    )
```

## Version 1

```{r}
final_data %>% 
  ggplot(aes(color = state)) +
  geom_line(aes(x = mid, y = cases)) +
  geom_point(aes(x = mid, y = cases), size = 0.75) +
  geom_line(aes(x = left_bound, y = bracket_line)) +
  geom_pointrange(aes(x = left_bound,
                      y = bracket_line,
                      ymin = bracket_line - 250,
                      ymax = bracket_line + 250,
                      ), fatten = 0) + 
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 90, 100), 
                     labels = c("0", "25", "50", "75", "90", "Unknown")) +
  labs(
    title = "Comparison of Florida and Tennessee\n by age on May 9, 2020",
    x = "Age",
    y = "Cases"
  )
```

## Version 2

```{r}
final_data %>% 
  ggplot(aes(color = state)) +
  geom_point(aes(x = mid, y = cases), size = 0.75) +
  geom_pointrange(aes(x = mid,
                      y = cases,
                      xmin = right_bound,
                      xmax = left_bound,
                      ), fatten = 0) + 
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 90, 100), 
                     labels = c("0", "25", "50", "75", "90", "Unknown")) +
  labs(
    title = "Comparison of Florida and Tennessee\n by age on May 9, 2020",
    x = "Age",
    y = "Cases")
```

# Possible Improvements?

- Show each states age ranges as text on the chart? Might clutter the chart
- I feel like showing the midpoints captures this information well, but it might not do so well for states with very large age spans
- Maybe don't show the unknowns since there's so little of them?
- Try to use the Census data to standardize to X cases / 100,000 people? The differing age brackets will be a problem here.