---
title: "COVID State Web Scraping"
output: html_document
---

Nevada Site Notes:

- They have a dashboard powered by Microsoft Power BI
- They also have [another dashboard](https://app.powerbigov.us/view?r=eyJrIjoiNDMwMDI0YmQtNmUyYS00ZmFjLWI0MGItZDM0OTY1Y2Y0YzNhIiwidCI6ImU0YTM0MGU2LWI4OWUtNGU2OC04ZWFhLTE1NDRkMjcwMzk4MCJ9) with slightly different sets of information

There are also [daily situation reports](https://nvhealthresponse.nv.gov/news-resources/daily-situation-reports/)

- total tested	
- total case	

- total tested today	
- total positive today	
- total death today	

- positive_race	
- positive_age	
- positive_gender	
- positivity rate	

- county details	

- total death	
- death_race	
- death_age	
- death_gender	

- comorbidities	
- total_hosp	
- hosp_race	
- hosp_age	
- hosp_gender	

```{r, message = FALSE, warning = FALSE }
library(tidyverse)
library(pdftools)
library(rvest)
```
``

```{r}
# The access dashboard doesnt seem to allow us to look at the data
# iowa = read_html("https://coronavirus.iowa.gov/pages/access")
  
iowa = pdf_text("../pdfs/IowaCOVID19_05042020.pdf")
```

```{r}
iowa
```

